Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-03-21 ms.tex
a little description of the A/B anti-correlation

@@

After experimenting with these configurations, we find the following pipeline steps are important:
\begin{itemize}
	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the read and electronic 1/f noise)
	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus)
	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
	\item An annulus aperture on the source (including the inner and outer edges of the hexagonal PSF) usually gives the best precision light curves
\end{itemize}

We also found reduction steps that had very little impact on the final photometric precision including
\begin{itemize}
	\item IPC corrections ($\lesssim 0.01$ ppm)
	\item Flat-fielding ($\lesssim 0.3$ ppm)
\end{itemize}
We summarize the lessons from the tests here.

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.69\columnwidth]{plot_mmm_showTemperatures_False_AB_sides.pdf}
\caption{Time Series plot through the CV3 photometric stability campaign for the A1 and B4 detectors.
The flux on the two detectors is highly anti-correlated so the flux is averaged between them for future analyses.
The anti-correlation likely arises due to the lamp source motion that preferentially couples with one fiber and then the other.
}\label{fig:CV3longTserAB}
\end{figure}

@@

After experimenting with these configurations, we find the following pipeline steps are important:
\begin{itemize}
	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read. This is  expected because more ramps reduce the 1/f and read noise, but the disparity (500 ppm versus 1200 ppm) is too large to be due to read noise alone.
	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus)
	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
	\item An annulus aperture on the source (including the inner and outer edges of the hexagonal PSF) usually gives the best precision light curves
\end{itemize}

We also found reduction steps that had very little impact on the final photometric precision including
\begin{itemize}
	\item IPC corrections ($\lesssim 0.01$ ppm)
	\item Flat-fielding ($\lesssim 0.3$ ppm)
\end{itemize}
